---
title: "Precip Data Download"
author: "Sarah B Dunn"
date: "3/23/2022"
output: html_document
---

```{r download-packages, include=FALSE}
library(riem) #package for getting weather from ASOS airport weather stations
library(sf)
library(mapview)
library(rayshader) #3D zooming plots
library(USAboundaries)
library(raster)
library(elevatr)
library(tmap)
library(tidyverse)
library(snotelr)
library(nhdplusTools)


knitr::opts_chunk$set(echo = TRUE)
```
#Precipitation Data downloads

First is some general code for downloading airport weather data, followed by code for downloading SNOTEL station data for the Poudre watershed.

## Download and data check for ASOS weather data
```{r}
#data acquisition

#view networks available
network <- riem_networks()

#read Colorado stations, bring in spatial component
co_stations <- riem_stations(network = 'CO_ASOS')%>%
  st_as_sf(., coords = c('lon', 'lat'), crs = 4326)
str(co_stations) # check that it says sf object at top to see that it is spatial

```


## Interactive Map
```{r}
#view where stations are in interactive map, more useful for initial exploration
mapview(co_stations)

glimpse(co_stations)
```


## Static Map

### Download DEM data and state boundary data
```{r}
co <- us_counties(states = 'Colorado')

co_elev <- elevatr::get_elev_raster(co_stations, z = 9)
```

### static mapping functions
```{r}
tm_shape(co) +
  tm_polygons(col = 'white')+
  tm_shape(co_stations) +
   tm_bubbles(size = 0.2, col = 'blue')
```

## Download a single site data
```{r}
fnl <- riem_measures(station = 'FNL',
                     date_start = '1985-01-01',
                     date_end =  '2000-01-01')
daily <- fnl %>%
  mutate(date =as.Date(valid)) %>%
  group_by(date)%>%
  summarize(daily_temp = mean(tmpf, na.rm = T))

ggplot(daily, aes(x = date, y =daily_temp))+
  geom_point()+
  scale_y_log10()
```


## Find precip data for Poudre Watershed

### Download WBD for catchment
```{r}
#use the NHD WBD to select sites

#define watershed point
start_point <- st_sfc(st_point(c(-105.208, 40.660170)), crs = 4326)
start_comid <- discover_nhdplus_id(start_point)

#get upstream flowlines
flowline <- navigate_nldi(list(featureSource = "comid", 
                               featureID = start_comid), 
                          mode = "upstreamTributaries", 
                          distance_km = 1000)
#subset files
subset_file <- tempfile(fileext = ".gpkg")
subset <- subset_nhdplus(comids = flowline$UT$nhdplus_comid,
                         output_file = subset_file,
                         nhdplus_data = "download", 
                         flowline_only = FALSE,
                         return_data = TRUE, overwrite = TRUE)
#
flowline <- subset$NHDFlowline_Network
catchment <- subset$CatchmentSP
waterbody <- subset$NHDWaterbody

## Or:

flowline <- sf::read_sf(subset_file, "NHDFlowline_Network")
catchment <- sf::read_sf(subset_file, "CatchmentSP")
waterbody <- sf::read_sf(subset_file, "NHDWaterbody")

#view

mapview(catchment)

```



### find snotel sites

```{r}
# download list of all snotel sites and convert to spatial object
snotel_sites <- snotel_info()%>%
    st_as_sf(., coords = c('longitude', 'latitude'), crs = 4269)

# select those that fall within catchment defined above
poudre_snotel <- st_join(x = snotel_sites, y = catchment, join = st_intersects, left = F)

# view map of snotel sites within the Poudre
mapview(poudre_snotel)
```

### Get data from sites

```{r}
#list sites from above
snotel_poudre_ID <- poudre_snotel$site_id

#download data as spatial objects
poudre_precip <- snotel_download(site_id = snotel_poudre_ID, internal = T )%>%
  st_as_sf(., coords = c('longitude', 'latitude'), crs = 4269)

mapview(poudre_precip)
```


## Data Analysis

This section needs to be moved to the data clean workflow

### subset data to after Cameron Peak Fire

```{r}
poudre_post_fire_precip <- poudre_precip %>%
  mutate(obs_date = as.Date(date))%>%
  filter(obs_date >= "2020-07-01")

ggplot(poudre_post_fire_precip, aes(x = obs_date, y = precipitation))+
  geom_point(group = 'site_name')
```

